%!TEX root = ../main.tex

\chapter{Introduction}
\label{chap:intro}

% Raman spectroscopy is a versatile analytical technique for the non-destructive characterization of molecules based on inelastic light scattering. Two experiments will be performed to demonstrate the capabilities of Raman spectroscopy.

% Firstly, the ethanol content of an unknown mixture of ethanol and water is to be determined. Different known mixtures will be used to establish a correlation between the measured signals and the ethanol concentration. In a second experiment, the isosbestic point as well as the temperature curve of water being subjected to changes in temperature, are determined.

% Before the setup, execution and results of the experiment are presented, the underlying physical principles of Raman spectroscopy are explained briefly. The assignment, description of the equipment and procedure and further details about the Lab Course are described in the given handbook \autocite{brauerApplicationRamanSpectroscopy2022}.

Raman spectroscopy is a versatile analytical technique for the non-destructive characterization of molecules based on inelastic light scattering. Two experiments will be performed to demonstrate the capabilities of Raman spectroscopy.  Optical diagnostics like Raman spectroscopy offer several advantages over conventional measurement techniques. A variety of process variables can be determined from a single measurement setup, as light molecule interactions are specific for each molecule and provide information about its energetic state. Thus, properties like molecular composition and temperatures can be determined. The non-destructive nature and high resolution make it suitable for in-situ measurements of chemical processes. 

Firstly, the ethanol content of an unknown mixture of ethanol and water is to be determined. Different known mixtures will be used to establish a correlation between the measured signals and the ethanol concentration. In a second experiment, the isosbestic point as well as the temperature curve of water being subjected to changes in temperature.

Before the setup, execution and results of the experiment are presented, the underlying physical principles of Raman spectroscopy are explained briefly. The assignment, description of the equipment and procedure and further details about the Lab Course are described in the given handbook \autocite{brauerApplicationRamanSpectroscopy2022}.
